Viscous Transport in Eroding Porous Media

### 2019-03-25 docs/transport/erosion_transport.tex
type the numerical method of exterior part

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral equation formulation} 
\label{sec:bies}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solving the BIE}
\label{sec:BIE}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shear stress}
\label{sec:shearStress}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TIME-STEPPING %%
\subsection{Time-stepping with the {\thL} method} 
\label{sec:timeStepping}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral equation formulation} 
\label{sec:bies}
Add an introduction why we do not use the double-layer potentials of Stokes equations but the double-layer potentials of Laplace equations to solve Stokes equation when we use Barycentric approach (or complex variable approach).
\subsubsection{Laplace's equations from $\Rdb^2$ to $\Cdb$ }

Let $\Omega$ be the domain of fluid. The boundary of $\Omega$ is $\Gamma$ and the outward normal vector on $\Gamma$ is ${\bf n_y}=(n_1,n_2)$.

Consider a Laplace's equations with Dirichlet boundary condition
\begin{equation}\label{Laplace}
  \begin{cases}
    \Delta {\bf u}=0, & \text{in}\,\,\, \Omega \in \Rdb^2;\\
    {\bf u}={\bf f}, & \text{on}\,\,\, \Gamma.
  \end{cases}
\end{equation}

Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.
The double-layer potential which solves \eqref{Laplace} is 
\begin{align*}
\D[\sigma]({\bf x})&=\frac{1}{2\pi}\displaystyle\int_{\Gamma} \frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma({\bf y})ds_y,
%\frac{1}{2\pi}\displaystyle\int_{\Gamma}\frac{\partial}{\partial {\bf n_y}} \log |{\bf x}-{\bf y}| \sigma({\bf y})ds_y,\\ \\
%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{{\bf r}\cdot{\bf n_y}}{\rho^2} \sigma({\bf y})ds_y\\ \\
%&=\frac{-1}{2\pi}\int_{\Gamma}\frac{n_1(x_1-y_1)+n_2(x_2-y_2)}{(x_1-y_1)^2+(x_2-y_2)^2} \sigma({\bf y})ds_y 
\numberthis\label{DLP:real}
\end{align*}
where $\sigma$ is the density function on the boundary $\Gamma$.

Consider a Cauchy integral 
\begin{equation}\label{CI}
v({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{\sigma({ y})}{{ y}-{ x}} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Cdb\setminus \Gamma.
\end{equation}
where ${ x}=x_1+ix_2$, $ { y}=y_1+iy_2$, ${ n_y}=n_1+i n_2$ and $d{ y}=i {n_y}ds_y$. It can be showed that 
the real part of the Cauchy integral in \eqref{CI} is equivalent to the double-layer potential in \eqref{DLP:real}.

\subsubsection{From Stokes DLP to Laplace DLPs}

Let ${\bf x}=(x_1,x_2), {\bf y}=(y_1,y_2)$. Then we have ${\bf r}={\bf x} - {\bf y}$ and $\rho=|\bf r|$.

The Stokes double-layer potential  is
\begin{equation}\label{StokesDLP1}
\D[\boldsymbol\sigma]({\bf x}):=\frac{1}{\pi}\int_{\Gamma}\left(\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\frac{{\bf r} \otimes {\bf r}}{\rho^2}\right) {\boldsymbol\sigma({\bf y})} d s_y.
\end{equation}
We could rewrite the Stokes DLP in terms of the Laplace DLP as
\begin{align*}\label{StokesDLP2}
\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
&-\frac{1}{2\pi}x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y-\frac{1}{2\pi}x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y. \numberthis
\end{align*}

@@

To calculate the shear stress, we need to know the gradient of double-layer potential in \eqref{StokesDLP2} 
\begin{align*}\label{SSLP}
\nabla\D[\boldsymbol\sigma]({\bf x})=\frac{1}{2\pi}\nabla\int_{\Gamma}&\frac{{\bf n_y}}{\rho^2}({\bf r} \cdot {\boldsymbol \sigma})ds_y+\frac{1}{2\pi}\nabla^2\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}({\bf y} \cdot{\boldsymbol \sigma})ds_y\\
&-\frac{1}{2\pi}\nabla\left(x_1 \nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_1ds_y\right)-\frac{1}{2\pi}\nabla\left(x_2\nabla\int_{\Gamma}\frac{{\bf r} \cdot {\bf n_y}}{\rho^2}\sigma_2ds_y\right). \numberthis
\end{align*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solving the BIE}
\label{sec:BIE}
\subsubsection{Interior Case}
Consider a Cauchy integral 
\begin{align}\label{CIFI}
\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{{ y}-{ x}} d{ y}
&=\begin{cases}
\,v(x), &{ x} \in \Omega,\\ 
\,0,  &{ x} \in \Cdb\setminus \bar{\Omega}.
\end{cases}
\end{align}
By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{{ y}-{ x}} d{ y}=1,$ we can rewrtie \eqref{CIFI} and get 
\begin{equation}
\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)}{{ y}-{ x}} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
\end{equation}
\begin{equation}\label{dNCI}
v'({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})}{(y- x)^2} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
\end{equation}
By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{dNCI} and get 
\begin{equation}
\frac{1}{2\pi i}\int_{\Gamma}\frac{v^-({ y})-v(x)-(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
\end{equation}

\subsubsection{Exterior case}
Consider a Cauchy integral formula for the exterior domain
\begin{align}\label{CIFE}
\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})}{{ y}-{ x}} d{ y}
&=\begin{cases}
\,v_{\infty}, &{ x} \in \Omega,\\ 
\,-v(x)+v_{\infty},  &{ x} \in \Omega^c,
\end{cases}
\end{align}
where $v_{\infty}=\displaystyle\lim_{x \to \infty}v(x)$.
\begin{equation}
\frac{1}{x-a}=\frac{-1}{2 \pi i} \int_{\Gamma}\frac{(y-a)^{-1}}{y-x} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
\end{equation}
\begin{equation}
\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-(y-a)^{-1}(x-a)v(x)}{y-x} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
\end{equation}
\begin{equation}
\frac{1}{2\pi i}\int_{\Gamma}\frac{v^+({ y})-v(x)-(y-a)^{-1}(x-a)(y-x)v'(x)}{(y-x)^2} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shear stress}
\label{sec:shearStress}
\subsubsection{Interior Case}
\begin{equation}\label{ddNCI}
v''({x})=\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})}{(y- x)^3} d{ y},\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
\end{equation}
By the identity of Cauchy Integral Formula $\displaystyle\frac{1}{2 \pi i}\int_{\Gamma}\frac{1}{( y- x)^n} d{ y}=0$ for integer n $\neq 1$, we can rewrtie \eqref{ddNCI} and get 
\begin{equation}
\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega.
\end{equation}
\subsubsection{Exterior case}
\begin{equation}
\frac{1}{2\pi i}\int_{\Gamma}\frac{2v^+({ y})-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2v''(x)}{(y-x)^3} d{ y}=0,\,\,\,\,\,\,\,\,\, \forall { x} \in \Omega^c.
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TIME-STEPPING %%
\subsection{Time-stepping with the {\thL} method} 
\label{sec:timeStepping}
